### 2019-12-11 docs/thesis-project/article.tex
updates

%%%%%%%%%%%%%%%%
% BEGIN HEADER %
%%%%%%%%%%%%%%%%
\title {Hives: File Survivability in P2P using Probabilistic Swarm Guidance
\thanks{This work has the support of the project MYRG2016-00097-FST of the University of Macau; by the Portuguese Fundação para a Ciência e a Tecnologia (FCT) through Institute for Systems and Robotics (ISR), under Laboratory for Robotics and Engineering Systems (LARSyS) project UID/EEA/50009/2019.}
}
\titlerunning{Hives}
\author{Francisco Barros, Daniel Silvestre \and Carlos Silvestre}
\authorrunning{F. Barros et al.}
\institute{Instituto Superior Técnico - Taguspark\newline Av. Prof. Doutor Cavaco Silva, 2744-016 Porto Salvo, Portugal
\email{fbarros@isr.ist.utl.pt, dsilvestre@isr.ist.utl.pt, csilvestre@umac.mo}\newline
\url{www.tecnico.ulisboa.pt}
}
\maketitle
%%%%%%%%%%%%%%
% END HEADER %
%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%
% BEGIN ABSTRACT %
%%%%%%%%%%%%%%%%%%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in 150--250 words.
\begin{keywords}Agents-based Systems; Cooperative Control; Peer-to-Peer; Cloud Storage; Distributed control; File Availability; Swarm Guidance;\end{keywords}
\end{abstract}
%%%%%%%%%%%%%%%%
% END ABSTRACT %
%%%%%%%%%%%%%%%%

@@

\subsection{Proposal Goals}\label{subsec:intro}
\begin{itemize}
    \item Implement a Tracker server with light-weight responsibilities:
        \SubItem{Act as peer discovery service for clients;}
        \SubItem{Act as an indexer for clusters of peers (Hives);}
        \SubItem{Track peer reputations;}
    \item Implement an erasure-code algorithm to ensure file persists in the Hive;
    \item Implement a trust system where:
        \SubItem Each peer gives feedback to the Tracker about his neighbors;
        \SubItem Tracker synthesizes the feedback and presents it to the client;
    \item Calculate the ideal steady-state distribution of file blocks, for a Hive, when:
        \SubItem{No trust history on a new peer is available;}
        \SubItem{Peer availability, reliability and other trust factors are known;}
    \item Hives converge to ideal block distribution in bounded-times using PSG;
    \item Efficiently update the PSG's Markov Chain as it changes over time;
    \item Balance the in-degree and out-degree of each peer such that:
        \SubItem{Message exchange overhead is minimal;}
        \SubItem{Any changes to the probability of file loss are negligible;}
        \SubItem{Hive availability, reliability, and, confidentiality are not compromised;}
        \SubItem{Hive is resilient to massive node failures and resistant to churn;}
    \item Extra miles may include:
        \SubItem{Peers can reconstruct Hives without Tracker intervention;}
        \SubItem{Peers trust their neighbors independently of Tracker;}
        \SubItem{Hives can leverage dedicated Cloud-Storage if they become unreliable;}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%
% END INTRODUCTION %
%%%%%%%%%%%%%%%%%%%%

@@

BlatAnt proved to accomplish its goals, quickly converging to stable overlays with bounded-diameter, even under very dynamic conditions \cite{sotart}, resulting in faster lookups due to the reduction of flood messages but also due to caching. Note that BlatAnt can leverage random walks such as the ones used in Gia for even less network overhead. BlatAnt also introduces optimizations over caching procedures; we do not review them here, because they are based on complex profile similarities and because caching is out of the scope of our proposal.

\subsection{Membership Management Framework - CYCLON}
\subsection{Cloud-Assisted P2P Protocol - CLOUDCAST}
\subsection{File Block Replication}
\subsection{Trust in Peer-to-Peer Networks}
\subsection{Probabilistic Swarm Guidance}
%%%%%%%%%%%%%%%%%%%%
% END RELATED WORK %
%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%
% BEGIN HEADER %
%%%%%%%%%%%%%%%%
\title {Hives: File Survivability in P2P using Probabilistic Swarm Guidance
\thanks{This work has the support of the project MYRG2016-00097-FST of the University of Macau; by the Portuguese Fundação para a Ciência e a Tecnologia (FCT) through Institute for Systems and Robotics (ISR), under Laboratory for Robotics and Engineering Systems (LARSyS) project UID/EEA/50009/2019.}
}
\titlerunning{Hives}
\author{Francisco Barros, Daniel Silvestre \and Carlos Silvestre}
\authorrunning{F. Barros et al.}
\institute{Instituto Superior Técnico - Taguspark\newline Av. Prof. Doutor Cavaco Silva, 2744-016 Porto Salvo, Portugal
\email{fbarros@isr.ist.utl.pt, dsilvestre@isr.ist.utl.pt, csilvestre@umac.mo}\newline
\url{www.tecnico.ulisboa.pt}
}
\maketitle
%%%%%%%%%%%%%%
% END HEADER %
%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%
% BEGIN ABSTRACT %
%%%%%%%%%%%%%%%%%%
\begin{abstract}
Peer-to-Peer (P2P) systems have emerged as a potential choice to build large scale distributed storage systems, at a fraction of the cost of the alternative cloud approaches, which have a better quality of service guarantees. We survey general-purpose P2P protocols, distributed file systems, cloud-assisted P2P protocols, and erasure-code algorithms. We then draft a solution for the problem of creating a bio-inspired P2P overlay to be used on a cloud-assisted P2P storage and backup system using probabilistic swarm guidance. We anticipate that our solution will have high network overhead, in order to provide self-healing properties to the files stored in the system.

\begin{keywords}Agents-based Systems; Cooperative Control; Peer-to-Peer; Cloud Storage; Distributed control; File Availability; Swarm Guidance;\end{keywords}
\end{abstract}
%%%%%%%%%%%%%%%%
% END ABSTRACT %
%%%%%%%%%%%%%%%%

@@

\subsection{Proposal Goals}\label{subsec:intro}
\begin{itemize}
    \item Implement a Tracker server with light-weight responsibilities:
        \SubItem{Act as peer discovery service for clients;}
        \SubItem{Act as an indexer for clusters of peers (Hives);}
        \SubItem{Track peer reputations;}
    \item Implement an erasure-code algorithm to ensure file persists in the Hive;
    \item Implement a trust system where:
        \SubItem Each peer gives feedback to the Tracker about his neighbors;
        \SubItem Tracker synthesizes the feedback and presents it to the client;
    \item Calculate the ideal steady-state distribution of file blocks, for a Hive, when:
        \SubItem{No trust history on a new peer is available;}
        \SubItem{Peer availability, reliability and other trust factors are known;}
    \item Hives converge to ideal block distribution in bounded-times using PSG;
    \item Efficiently update the PSG's Markov Chain as it changes over time;
    \item Balance the in-degree and out-degree of each peer such that:
        \SubItem{Message exchange overhead is minimal;}
        \SubItem{Any changes to the probability of file loss are negligible;}
        \SubItem{Hive availability and reliability are not compromised;}
        \SubItem{Hive is resilient to massive node failures and resistant to churn;}
    \item Extra miles may include:
        \SubItem{Peers can reconstruct Hives without Tracker intervention;}
        \SubItem{Peers trust their neighbors independently of Tracker;}
        \SubItem{Hives can leverage dedicated Cloud-Storage if they become unreliable;}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%
% END INTRODUCTION %
%%%%%%%%%%%%%%%%%%%%

@@

BlatAnt proved to accomplish its goals, quickly converging to stable overlays with bounded-diameter, even under very dynamic conditions \cite{sotart}, resulting in faster lookups due to the reduction of flood messages but also due to caching. Note that BlatAnt can leverage random walks such as the ones used in Gia for even less network overhead. BlatAnt also introduces optimizations over caching procedures; we do not review them here, because they are based on complex profile similarities and because caching is out of the scope of our proposal.\newline

\textbf{CYCLON} \cite{cyclon} is a protocol that emerges as an inexpensive solution to the maintenance of gossip-based unstructured overlays. CYCLON is useable even in highly dynamic environments, providing peer degree symmetry, low diameter, low clustering, resilience to churn and massive node failures, in a fully decentralized manner. One fundamental issue of unstructured networks is to avoid partitioning. One naive solution would be for each peer to keep a view of all the peers in the network and create connections has needed, but that solution is not scalable.

The protocol is simple. It consists of having each peer keeping an ever-changing, partial view, with fixed-size \textit{c}, of the network in a structure called \textit{neighbors}. Periodically and independently, a contacts a random neighbor to exchange acquaintances. This process is called \textit{shuffling}. During a shuffle, a peer \textit{i}, first increments the age of all his known neighbors by one. Then, selects the oldest of all his neighbors, \textit{j}, and $l-1$ other random neighbors, forming \textit{s}. Then \textit{i} replaces \textit{j}'s network address by his own and sets his age to zero, in \textit{s}. After that, \textit{i} sends \textit{s} to \textit{j} and waits for \textit{j} to reply with \textit{s'}. Unlike \textit{s}, \textit{s'} is composed of a purely random subset of \textit{j}'s neighbors, without any age modifications. Upon reception of subsets \textit{s} and \textit{s'}, \textit{j} and \textit{i}, respectively, update their \textit{neighbors} by first using any empty slots in their partial views and then by replacing entries which they sent to the other, i.e., if \textit{i} has no more slots, he replaces, in its \textit{neighbors} structure, the entries that he sent in \textit{s} to \textit{j}, with the ones he received in \textit{s'} from \textit{j}. Note that, after \textit{i} initiates a shuffle with \textit{j}, \textit{i} becomes \textit{j}'s neighbor, but \textit{j} is no longer a neighbor to \textit{i}, i.e., the neighboring relation between \textit{i} and \textit{j} is reversed. Unlike many protocols, CYCLON links between peers are not bidirectional.

The age is essential in the shuffling algorithm, for two reasons. First, it limits the lifetime of each peer in \textit{neighbors} structures, which globally bounds the number of existing pointers to them, it also limits the time each peers' addresses are passed around until they are selected as shuffling targets, resulting on a more up-to-date overlay as well as uniform distribution of each peers' addresses over the network.

When a peer leaves the overlay for any reason, the remaining peers may have to remove him from their \textit{neighbors} structure. Timely removal is fundamental for the robustness of the overlay.  CYCLON uses passive detection. Whenever a peer \textit{i} contacts \textit{j} for shuffling and obtains no response it assumes \textit{j} is disconnected and removes it from his \textit{neighbors}. Since the time for \textit{i} to contact \textit{j} is bounded by the age property in \textit{neighbors}, detection is accelerated.

CYCLON simulations show that the average path length and clustering coefficient, for various configurations, converged to values similar to those found in random graphs, i.e., converged to small-diameter topologies with low clustering. Gossip-based protocols often have high clustering, which is undesirable, since that may indicate an increased amount of redundant messages passing through the network and a higher chance of network partitioning. Another exciting result of CYCLON is that the average path length increased logarithmically, and clustering decreased exponentially, as the number of peers in the network increased, hence demonstrating scalability and increased robustness.

The authors also propose a join method that does not disrupt the randomness of the obtained overlays, while simultaneously making new peers indistinguishable from old ones. Whenever \textit{i} wishes to join the overlay, he contacts one peer \textit{j} already in the overlay who initiates \textit{c} random-walks with time-to-live (TTL) equal to the average path length of the overlay. The peer \textit{k} where the random-walk ends, replaces one of his \textit{neighbors} entries with \textit{i} network address, setting \textit{i} age set to zero and sends the replaced entry to \textit{i}. Note that even if some of the random walks do not complete due to byzantine failures, \textit{i} will remain connected to the overlay and will eventually find new acquaintances.

We conclude by reinforcing the idea that CYCLON is a scalable and robust solution for peer-sampling, providing good self-healing and self-organization capabilities without complex algorithms or apparent downsides. In a way, it relates to BlatAnt since the proposal passively bounds the diameter of the network.

\subsection{Cloud-Assisted P2P Protocol - CLOUDCAST}
\subsection{File Block Replication}
\subsection{Trust in Peer-to-Peer Networks}
\subsection{Probabilistic Swarm Guidance}
%%%%%%%%%%%%%%%%%%%%
% END RELATED WORK %
%%%%%%%%%%%%%%%%%%%%
